An Improved ANS Transaction Template

### 2018-01-25 paper.tex
adding ref case description

Other hypothesis will be explored in the future, such as maintaining the ideal
stage of the cascade through a tunning of the cuts values $\theta_{i}$ of each
stage of the cascade, or maintaining $\alpha\beta = const$ as described in
\cite{walker2017}.

>>>>

Other hypothesis will be explored in the future, such as maintaining the ideal
stage of the cascade through a tuning of the cuts values $\theta_{i}$ of each
stage of the cascade, or maintaining $\alpha\beta = const$ as described in
\cite{walker2017}.

Note that as a consequence of our design method, the cascade product and tail
assay will not necessary match the targeted values, and usually slightly over
enrich and over strip the product and the tail.

\section{The experiment}

As explain previously, the goal of this work is to assess the rate of the HEU
production using enrichment cascade designed within the JCPOA agreement
constrains. For this work two different cases will be investigated and compare
to the reference case.

\subsection{Reference Case}
The reference case corresponds to a cascade design include all the 5060
centrifuges available within JCPOA targeting an enriched product at $90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium. 
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.

\subsection{Case 1}
\subsection{Case 2}

Both case 1 and 2 will be simulation without and with tail recycling. In the
tail recycling cases, the tails of the cascade level $N$ are blended in the feed
of cascade level $N-1$.
